plots with prolactin

### 2020-01-05 analysis/16_PRL.Rmd
new combined PRL image

```{r hormone}
p1 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc)) +
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) +
    theme_B3() +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin (ng/mL)", x = NULL) +
    guides(fill = FALSE, alpha = FALSE,
         color = guide_legend(order=1)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "increasing time >>", y = "prolactin (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.8) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.8) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.6) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.4) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.4) + 
  ylim(c(-10,120)) 
p1
```

@@

>>>>

```{r hormone}
p1 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc)) +
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) +
    theme_B3() +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin (ng/mL)", x = NULL) +
    guides(fill = FALSE, alpha = FALSE,
         color = guide_legend(order=1)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "increasing time >>", y = "prolactin (ng/mL)")
p1

p1 +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.8) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.8) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.6) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.4) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.4) + 
  ylim(c(-10,120))

@@

```{r hormonesandgenes}
plot_grid(p1 + theme(legend.position ="none",
                     axis.title.x = element_blank(),
                     axis.text.x = element_blank()),
          p2 + theme(legend.position = c(0.85,0.3)) +
            labs(subtitle = NULL) +
  annotation_custom(control, ymin = 13.5, ymax = 15.5, xmin = -7.5) +
  annotation_custom(bldg, ymin = 13.5, ymax = 15.5, xmin = -5.5) +
  annotation_custom(lay, ymin = 13.5, ymax = 15.5, xmin = -3.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15.5, xmin = -1.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15.5, xmin = 0.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15.5, xmin = 2.5) +
  annotation_custom(hatch, ymin = 13.5, ymax = 15.5, xmin = 4.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15.5, xmin = 6.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15.5, xmin = 8.5), 
          nrow = 2,rel_heights = c(0.4,0.6)) 
```
